Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-12 Grassmannian_cells.tex
Lemma 4.8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$GL_n$ Action on Arrows of $K(n)$}
Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$GL_n$ Action on Arrows of $K(n)$}
Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,(g.M)_{a_i})$ with $(g.M)_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
  \[\theta_2\circ (g.M)_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(N_{a_j}\circ\theta_1)=(g.N)_{a_i}\circ\theta_1\]
  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}
